Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-26 paper/paper.tex
pass

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our evaluation.  Column ``Name'' shows the
name of the attack, column ``Source'' shows the source where we
obtained data to reproduce the attack (see
Section~\ref{subsec:malicious-traffic}), column ``Type'' shows the
kind of attack, column ``Protocol'' shows the name of the protocol
explored in the attack, and column ``Ground Truth'' shows the rule
options to capture the attack. The rationale for the selection were
(1) to cover attacks with different characteristics, (2) to cover
attacks of various protocols, and (3) to explore different features of
\tname. As for (1), the selection includes attacks of the following
types: Denial-of-Service (DoS), Active Reconnaissance (AREC),
Privilege escalation (PESC), and Remote Code Execution (RCE). Note
that the distribution of attacks is not uniform across types and
protocols as these distributions are not uniform in practice. For
example, as per~\cite{emerging-threats-open}, RCE are the most
prevalent type of attacks today.\Mar{please, confirm} \Luc{Nao da
para afirmar isso, as regras nao contem essa informacao. A classificacao
das regras eh bem generica, por exemplo: "web-application-attack".} Columns
``Protocol'' and ``Ground Truth'' indicate, respectively, that we
analyzed attacks of different protocols and analyzed different
features of \tname.

>>>>

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our evaluation.  Column ``Name'' shows the
name of the attack, column ``Source'' shows the source where we
obtained data to reproduce the attack (see
Section~\ref{subsec:malicious-traffic}), column ``Type'' shows the
kind of attack, column ``Protocol'' shows the name of the protocol
explored in the attack, and column ``Ground Truth'' shows the rule
options to capture the attack. The rationale for the selection were
(1) to cover attacks with different characteristics, (2) to cover
attacks of various protocols, and (3) to explore different features of
\tname. As for (1), the selection includes attacks of the following
types: Denial-of-Service (DoS), Active Reconnaissance (AREC),
Privilege escalation (PESC), and Remote Code Execution (RCE). Note
that the distribution of attacks is not uniform across protocols as
these distributions are not uniform in practice---http attacks are
prevalent.
